Measuring neutron star tidal deformability with Advanced LIGO: a Bayesian analysis of mixed binary observations

### 2016-07-11 Paper/paper.tex
description of new lambda CI plots

Finally, we investigate the statistical uncertainties associated with
$\lambdans$ measurements. We use $90\%$ confidence intervals as our measure of
the same. The left column of 
Fig.~\ref{fig:TT_LambdaError_vs_N_L500_2000_CI90_0_AllInOne} shows results
under paradigm A. In each panel
we show the width of the $90\%$ confidence interval measured from $N$ events
(with $N$ on the $x$-axis), normalized by the true value of $\lambdans$ for
the population. In gray are shown results from each of $100$ population
realizations, with the single population highlighted in color corresponding
to the one we focused on in 
Fig.~\ref{fig:TT_Lambda_vs_N_L800_CI90_0}-\ref{fig:TT_Lambda_vs_N_CI90_0}.
The inset shows the same, except that the ordinate is {\it not} normalized by
the true value of $\lambdans$. From top to bottom, the population $\lambdans$
decreases from $\lambdans=2000\rightarrow 500$, corresponding to decreasingly
deformable NSs with softer equations of state. We observe the following:
(i) for moderately-hard to hard equations of state with $\lambdans\geq 1000$,
we can constrain $\lambdans$ within $\pm 50\%$ using only $10-20$ events, and
within $\pm 25\%$ with $25-40$ events; (ii) for softer equations of state with
$\lambdans<1000$, we will achieve the same accuracy with $20-30$ and $50+$ 
events, respectively; and (iii) for the first $5$ or so observations, our
measurement confidence spans the entire prior allowed range 
$\lambdans\in[0,4000]$, as shown by the plateauing towards the left edge in
each panel's inset.
% 
In the right column, each panel panel is identical to its corresponding left
one, with the difference that populations are drawn under paradigm B, which
does {\it not} allow for BH masses to fall within the mass-gap. We find that
for NSs with $\lambdans\leq 1000$, it would take $25-40$ events to
constrain $\lambdans$ within $\pm 50\%$ and $50+$ events to constrain it
within $\pm 25\%$. This is somewhat slower than paradigm A, as is to be
expected since here we preclude the lowest mass-ratios, which correspond to
signals with largest tidal signatures. For $\lambdans>1000$ we find that we
can constrain $\lambdans$ within $\pm 50\%$ with a similar number of events as
for paradigm A, but will need more ($30-40$, as compared to $25-40$) events
to further constrain it to within $\pm 25\%$ of the true value.
%

>>>>

Finally, we investigate the statistical uncertainties associated with
$\lambdans$ measurements. We use $90\%$ confidence intervals as our measure of
the same. First, we draw an ensemble of a hundred populations each for
$\lambdans=\{500,1000,1500,2000\}$. For each population $i$ in each ensemble,
we construct
its $90\%$ confidence interval $[{\lambdans^{90\%}}_{i-},{\lambdans^{90\%}}_{i+}]$.
Next, we construct the interval $[X^-,Y^-]$ that contains ${\lambdans^{90\%}}_{i-}$
for $90\%$ of the populations in each ensemble; and similarly $[X^+,Y^+]$
for ${\lambdans^{90\%}}_{i+}$. Finally, in the left panel of 
Fig.~\ref{fig:TT_LambdaError_vs_N_L500_2000_CI90_0_AllInOne}, we show the
conservative width $|Y^+ - X^-|$ that contains the $90\%$ confidence
intervals for $90\%$ of all populations in each ensemble~\footnote{Drawn
under paradigm A.}.
% 
% In each panel
% we show the width of the $90\%$ confidence interval measured from $N$ events
% (with $N$ on the $x$-axis), normalized by the true value of $\lambdans$ for
% the population. In gray are shown results from each of $100$ population
% realizations, with the single population highlighted in color corresponding
% to the one we focused on in 
% Fig.~\ref{fig:TT_Lambda_vs_N_L800_CI90_0}-\ref{fig:TT_Lambda_vs_N_CI90_0}.
% The inset shows the same, except that the ordinate is {\it not} normalized by
% the true value of $\lambdans$. 
% 
From top to bottom, the population $\lambdans$
decreases from $\lambdans=2000\rightarrow 500$, corresponding to decreasingly
deformable NSs with softer equations of state. We observe the following:
(i) for moderately-hard to hard equations of state with $\lambdans\geq 1000$,
we can constrain $\lambdans$ within $\pm 50\%$ using only $10-20$ events, and
within $\pm 25\%$ (marked by black circles) with $25-40$ events; (ii) for softer 
equations of state with
$\lambdans<1000$, we will achieve the same accuracy with $20-30$ and $50+$ 
events, respectively; and (iii) for the first $5$ or so observations, our
measurement spans the entire prior allowed range:
$\lambdans\in[0,4000]$, as shown by the plateauing of the $90\%$ 
confidence intervals towards the left edge to $90\%$ of $4000$, i.e. $3600$.
% 
The right panel in Fig.~\ref{fig:TT_LambdaError_vs_N_L500_2000_CI90_0_AllInOne}
is identical to the left one, with the difference that populations are drawn
under paradigm B, which does {\it not} allow for BH masses to fall within
the mass-gap. We find that
for NSs with $\lambdans\leq 1000$, it would take $25-40$ events to
constrain $\lambdans$ within $\pm 50\%$ and $50+$ events to constrain it
within $\pm 25\%$. This is somewhat slower than paradigm A, as is to be
expected since here we preclude the lowest mass-ratios, which correspond to
signals with largest tidal signatures. For $\lambdans>1000$ we find that we
can constrain $\lambdans$ within $\pm 50\%$ with a similar number of events as
for paradigm A, but will need more ($30-40$, as compared to $25-40$) events
to further constrain it to within $\pm 25\%$ of the true value.
% 
Under either paradigms, we find that measuring $\lambdans$ better than
$25\%$ will require $\mathcal{O}(10^2)$ observations of disruptive NSBH
mergers.
